---
title: "eda"
author: "Alberto Macías"
date: "5/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Predicting the price of your car}

Data for this project was downloaded from kaggle and can be consulted in [here](https://www.kaggle.com/nehalbirla/vehicle-dataset-from-cardekho).

```{r, include=F}
library(dplyr)
library(ggplot2)
library(caret)
```

```{r}
df <- read.csv("./data/car data.csv", header = T)
df <- df[,-1]
df$age = 2021 - df$Year
df <- df %>% filter(Fuel_Type != "CNG")
df$Fuel_Type <- as.factor(df$Fuel_Type)
df$Seller_Type <- as.factor(df$Seller_Type)
df$Transmission <- as.factor(df$Transmission)
df$Price_difference <- df$Present_Price - df$Selling_Price
```

## Spliting dataset and performing some EDA
```{r}
set.seed(28)
inTrain <- createDataPartition(df$Present_Price, p=0.8, list = F)
trainig <- df[inTrain,]
testing <- df[-inTrain,]
```

```{r}
str(trainig)
summary(trainig)
trainig <- na.omit(trainig)
```

```{r}
trainig %>% ggplot(aes(x=Selling_Price)) +
            geom_density()+
            labs(title="Selling price of cars")

trainig %>% ggplot(aes(x=Present_Price)) +
            geom_density()+
            labs(title="Present price of cars")

trainig %>% ggplot(aes(x=Price_difference))+
            geom_density()+
            labs(title = "Difference between selling price and present price")

trainig %>% ggplot(aes(x=age))+
            geom_density()+
            labs(title = "Age of cars")

trainig %>% ggplot(aes(x=Kms_Driven))+
            geom_density()+
            labs(title = "Kilometes driven")

trainig %>% ggplot(aes(Fuel_Type))+
            geom_bar()+
            labs(title="Fuel Type")

trainig %>% ggplot(aes(Seller_Type))+
            geom_bar()+
            labs(title="Seller Type")

trainig %>% ggplot(aes(Transmission))+
            geom_bar()+
            labs(title="Transmission")

trainig %>% ggplot(aes(x=Owner))+
            geom_histogram(binwidth = .9)+
            labs(title="Number of owners")
```

```{r}
trainig %>% ggplot(aes(x=age, y=Present_Price))+
            geom_point()+
            labs(title = "Price vs Age")

trainig %>% ggplot(aes(x=Kms_Driven, y=Present_Price))+
            geom_point()+
            labs(title = "Price vs Kilometers Driven")

trainig %>% ggplot(aes(x=Present_Price, fill=Fuel_Type))+
            geom_density(alpha=.6)+
            labs(title="Price by Fuel Type")

trainig %>% ggplot(aes(x=Present_Price, fill=Seller_Type))+
            geom_density(alpha=.6)+
            labs(title="Price by Seller Type")

trainig %>% ggplot(aes(x=Present_Price, fill=Transmission))+
            geom_density(alpha=.6)+
            labs(title="Price by Transmission")

```

### Regression model
```{r}
trainig <- trainig %>% select(Present_Price, age, Fuel_Type, Kms_Driven,
                              Transmission, Seller_Type, Owner)
```

```{r}
model <- lm(Present_Price~., data=trainig)
summary(model)
plot(model)
```

It seems that there is still some influence between the fitted values and the residuals. This may be explained by the lack of other variables that may increase the price of cars, such as some luxury items that these may include and are not present in the data.

```{r}
testing <- testing %>% select(Present_Price, age, Fuel_Type, Kms_Driven,
                              Transmission, Seller_Type, Owner)
```

```{r}
pred <- predict(model, testing)
values <- data.frame(real_values = testing$Present_Price, 
                     pred_values = pred,
                     residuals = testing$Present_Price - pred)
(mse <- sqrt(sum(values$residuals^2)))
```

Linear regression doesn't seem to have a good performance, so I try with random forest regression.

## Random Forest Regression

```{r}
model_rf <- train(Present_Price~., data = trainig, method="rf",
                  trControl = trainControl("cv", number = 3))
pred_rf <- predict(model_rf, testing)
values$pred_values_rf <- pred_rf
values$residuals_rf <- values$real_values - values$pred_values_rf
(mse_rf <- sqrt(sum(values$residuals_rf)))
```

Random forest model seems to have a better performance out of sample

```{r}
app_data <- rbind(trainig, testing)
write.csv(app_data,file = "./predicting_prices/app_data.csv")
```

