---
title: "Predict the price of your car - Reproducible Pitch"
author: "Alberto Macías"
date: "5/19/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(dplyr)
library(caret)
library(randomForest)
```


## Predicting prices

The web application may be consulted in [here](https://albertomacias.shinyapps.io/predicting_prices/). 

The purpose of this application is that people that want to sell their car, can compute an approximated price depending on a few variables. The variables that are being used are:

- Age of the car  
- Fuel Type  
- Kilometers Driven  
- Transmission  
- Seller Type  
- Number of previous owners  

The data for this project was downloaded from Kaggle and may be consulted [here](https://www.kaggle.com/nehalbirla/vehicle-dataset-from-cardekho).

## Model used

For this project, first was considered a linear regression model but because of the poor performance was considered a random forest regression.

```{r, echo=TRUE}
app_data <- read.csv("./data/car data.csv")
app_data <- app_data %>% mutate(age = 2021-Year) %>%
            select(Present_Price, age, Kms_Driven, Fuel_Type,
                   Seller_Type, Transmission, Owner)
app_data <- na.omit(app_data)
model <- train(Present_Price~., data = app_data, method="rf",
                      trControl = trainControl("cv", number = 3))
```

The process of the exploratory data analysis and the model selection may be consulted in my [github repository](https://github.com/albert2828/coursera_ddp_final_project).

## ui.R file

The following is part of the ui.R code

```{r, echo=TRUE}
#library(shiny)
#shinyUI(fluidPage(
#    titlePanel("Compute the price of your car"),
#    sidebarLayout(
#        sidebarPanel(
#            sliderInput("age",
#                        "Age of your car:",
#                        min = 1,
#                        max = 50,
#                        value = 5),
#            selectInput(inputId = "Fuel_Type", label = "Select the type of fuel your cars uses",
#                        choices = c("Petrol", "Diesel"),
#                        selected = "Petrol"),
#            sliderInput("Kms_Driven",
#                        "Kilometers Driven",
#                        min = 1,
#                        max = 500000, 
#                        value = 5000),
#            selectInput("Transmission", "Select the type of Transmission of your car",
#                        choices = c("Automatic",  "Manual"),
#                        selected = "Automatic"),
#            selectInput("Seller_type", "Do you want to sell it yourseld or by a third party?",
#                   choices = c("Dealer", "Individual"),
#                   selected =" Dealer"),
#            selectInput("Owner", "Number of previous owners",
#                        choices = 0:5,
#                        selected = 0),
#            submitButton("Submit")
#        ),
#        mainPanel(
#            h3("Aproximated price of your car"),
#            textOutput("pred"),
#            br(),
#            p("This app is made so you can aproximate the price of your car if you want to sell it"),
#            p("You only need to fill a few gaps"),
#            tags$ul(
#                tags$li("Age: age of your car"),
#                tags$li("Fuel Type: Petrol or Diesel (for the moment we are not prepared for electric cars)"),
#                tags$li("Killometers Driven: if your cars runs in miles, multiply miles by 1.60934"),
#                tags$li("Transmission: Automatic or Manual"),
#                tags$li("Do you plan to sell it yourself of to go to an agency?"),
#                tags$li("Number of owners: How may persons have had the car before you?")
#            ),
#            p("Finally, just click the Submit buttom!"),
#            )
#        )
#    )
#)
```

## server.R

The following is part of the code of the server.R file

```{r, echo=TRUE}
#library(shiny)
#shinyServer(function(input, output) {
#    library(caret); library(randomForest)
#    app_data <- read.csv("app_data.csv")
#    app_data <- app_data[,-1]
#    model <- train(Present_Price~., data = app_data, method="rf",
#                      trControl = trainControl("cv", number = 3))
#    modelpred <- reactive({
#        new_data <- data.frame(age=input$age,
#                               Fuel_Type=input$Fuel_Type,
#                               Kms_Driven = input$Kms_Driven,
#                               Transmission = input$Transmission,
#                               Seller_Type=input$Seller_type,
#                               Owner=as.numeric(input$Owner))
#        predict(model, newdata = new_data)
#    })
#    output$pred <- renderText({
#        paste("$",floor(1000*modelpred()))
#    })
#})
```

